Literature

### 2015-08-04 literature/literature.Rmd
added more literature

>>>>

```{r, echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
cat(paste0("##", citet(refs[["xie_discriminative_2015"]])))
```

Consecutive n-grams + random forests. Good n-gram reference: Manning and Schuetze, 1999. Benchmark with other methods.

```{r, echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
cat(paste0("##", citet(refs[["behnam_geometric_2013"]])))
```

HGT as the example of phenomenon missed by alignment-based phylogenetics.

Critique of $D^2$ statistic and introduction of its variant. Introduction of bichromatic closest
pair. Article focused on the speed.
